---
title: "Walkthrough Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{working_example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this example, an example data set is used to walk through a calculation of rate change for illustration.

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
library(kableExtra)
library(DT)
```


The example below shows a subset of a cedant's data where there are two insureds, "berlin" and "frankfurt" which have been written in 2019 and renewed in 2020. The names vary slightly from year to year. We can use one of the pre-processing functions `standardise_names` to create a key from insured names which can be used to link renewals.

```{r}
library(ograrc)

example <- data.table::data.table(
              insured = c("berlin", "frankfurt" , "berlin, inc", "frankfurt inc") , 
              inception = c("01/01/2019" , "01/06/2019" , "01/01/2020", "01/06/2020"),   
              premium = c(100,120,110,100),
              Limit = c(1000, 500, 1000,400),
              attach = c(100,100,50,50),
              industry = c("retail" , "pharma" , "retail" , "pharma")
              
              )
```


```{r warning=FALSE}
kableExtra::kable(example)
```


### Simple Data Cleansing

We can call `convert_data_type` to convert fields to correct data types for R.

```{r warning=FALSE}
str(example)
example <- convert_data_type(example, num_cols = c("premium" , "Limit", "attach"), date_cols = "inception" , factor_cols = "industry" )

str(example)
```

### Additional Pre-processing

Next we can preprocess the data and add additional features required for calculating RARC by policy quarter. This includes:

- adding a feature for QY in the form YYYYQQ
- standardising the names and creating a field `std_Insured_name` to generate a key which can be used to link renewals.
- Note : an alternative would be to use a repeating part of policy_ids to also generate a key


### Adjusting For Limit/Attachment changes

Lastly we require a feature for LEV ( Limited Expected Value) which will be used to adjust rate changes for changes in limit and attachment point. The LEV is calculated via a lognormal curve with parameters mu and sigma. K signifies the moment of the distribution.

```{r warning=FALSE}
example[, policy_year := lubridate::year(`conform  inception`) ]
example <- add_qy(example , policy_year, `conform  inception` , add_miss= TRUE)

example <- standardise_names(example , name_col = "insured" , clean_patt = "inc")
example <- calc_lev(example, Limit , attach , k=1 , mu =15.2, sigma=1.74)
```

```{r warning=FALSE, include=FALSE}
kableExtra::kable(example)
```


### Calculate RARC

Now we can call `tidy_rarc` function to calculate rate change and return a long form dataset of results
 
```{r warning=FALSE}
library(data.table)
example_rarc <- tidy_rarc(example, premium_type = "premium", col_key = c("insured", "industry"))

kableExtra::kable(example_rarc)
```

### Summarise RARC by qtr and industry

It is now easy to summarise the detailed output by whatever segmentation is required - shown below by policy period


```{r warning=FALSE}
output <-example_rarc[ , .(Policy_Count = .N , Premium = sum(Premium), `OG Wtd RARC` = sum(Restated_Expiry_Wt)/sum(Restated_Expiry) ,
                                                mean_RARC_all = mean(RARC) -1,
                                                sd_err_rarc =sd(RARC)/sqrt(.N)), by= .(Policy_Period, industry) ][
                                                    order(Policy_Period, industry)][Policy_Period=="2020Q1"]
kableExtra::kable(output)
```


















